---
title: "Korean Sightseeing"
author: "Richie Liew"
date: "Nov 13, 2016"
output:
  pdf_document: default
  html_document: default
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=10, fig.height=6, fig.path='Figures2/', echo=FALSE, warning=FALSE, message=FALSE)
```

```{r}
library(leaflet)
```

### Have Fun in South Korea
Here are a list of 10 places of interest if you are visiting South Korea:

1. [Gyeongbokgung Palace](#gyeongbokgung-palace)
2. [Bukhansan National Park](#bukhansan-national-park)
3. [Changdeokgung Palace](#changdeokgung-palace)
4. [Myeongdong Shopping Street](#myeongdong-shopping-street)
5. [N Seoul Tower](#n-seoul-tower)
6. [Hangang Park](#hangang-park)
7. [National Museum of Korea](#national-museum-of-korea)
8. [Nami Island](#nami-island)
9. [Silk Fall Jiri Mountain](#silk-fall-jiri-mountain)
10. [Kwanghan Pavilion](#kwanghan-pavilion)

### Gyeongbokgung Palace
```{r}
# Gyeongbokgung Palace
# 161 Sajik-ro, Sejongno, Jongno-gu, Seoul, South Korea
m <- leaflet() %>%
  addTiles() %>%  
  addMarkers(lng=126.976684, lat=37.577362, popup="Gyeongbokgung Palace")
m  # Print the map
```
[TOP](#have-fun-in-south-korea)

### Bukhansan National Park
```{r}
# Bukhansan National Park
# 262 Bogukmun-ro, Hyoja-dong, Seongbuk-gu, 서울특별시 South Korea
m <- leaflet() %>%
  addTiles() %>%  
  addMarkers(lng=126.83202, lat=37.65836, popup="Bukhansan National Park")
m  # Print the map
```
[TOP](#have-fun-in-south-korea)

### Changdeokgung Palace
```{r}
# Changdeokgung Palace
# 99, Yulgok-ro, Jongno-gu, Seoul 03072, South Korea
m <- leaflet() %>%
  addTiles() %>%  
  # Specify coordinates for Damascus
  addMarkers(lng=126.976684, lat=37.577362, popup="Changdeokgung Palace")
m  # Print the map
```
[TOP](#have-fun-in-south-korea)

### Myeongdong Shopping Street
```{r}
# Myeongdong Shopping Street
# Myeong-dong, Jung-gu, Seoul, South Korea
m <- leaflet() %>%
  addTiles() %>%  
  # Specify coordinates for Damascus
  addMarkers(lng=126.98583, lat=37.55998, popup="Myeongdong Shopping Street")
m  # Print the map
```
[TOP](#have-fun-in-south-korea)

### N Seoul Tower
```{r}
# N Seoul Tower
# 105, Namsangongwon-gil, Yongsan-gu, Seoul, South Korea
m <- leaflet() %>%
  addTiles() %>%  
  # Specify coordinates for Damascus
  addMarkers(lng=126.989297, lat=37.550947, popup="N Seoul Tower")
m  # Print the map
```
[TOP](#have-fun-in-south-korea)

### Hangang Park
```{r}
# Hangang Park
# Nodeul-ro, Dangsan 2(i)-dong, Yeongdeungpo-gu, Seoul, South Korea
m <- leaflet() %>%
  addTiles() %>%  
  # Specify coordinates for Damascus
  addMarkers(lng=126.889842, lat=37.545629, popup="Hangang Park")
m  # Print the map
```
[TOP](#have-fun-in-south-korea)

### National Museum of Korea
```{r}
# National Museum of Korea
# 137 Seobinggo-ro, Yongsan-gu, Seoul 04383, South Korea
m <- leaflet() %>%
  addTiles() %>%  
  # Specify coordinates for Damascus
  addMarkers(lng=126.994917, lat=37.520596, popup="National Museum of Korea")
m  # Print the map
```
[TOP](#have-fun-in-south-korea)

### Nami Island
```{r}
# Nami Island (남이섬)
# 1 Namisum-gil, Namsan-myeon, Chuncheon, Gangwon-do, South Korea
m <- leaflet() %>%
  addTiles() %>%  
  # Specify coordinates for Damascus
  addMarkers(lng=127.525807, lat=37.789935, popup="Nami Island (남이섬)")
m  # Print the map
```
[TOP](#have-fun-in-south-korea)

### Silk Fall Jiri Mountain
```{r}
# Silk Fall, Jiri Mountain (지리산 뱀사골 실비단폭포)# 
# 320-2, Jirisan-daero, Sancheong-gun, Gyeongsangnam-do
m <- leaflet() %>%
  addTiles() %>%  
  # Specify coordinates for Damascus
  addMarkers(lng=127.817831, lat=35.243835, popup="Silk Fall, Jiri Mountain (지리산 뱀사골 실비단폭포)")
m  # Print the map
```
[TOP](#have-fun-in-south-korea)

### Kwanghan Pavilion
```{r}
# Kwanghan Pavilion
# 137 Seobinggo-ro, Yongsan-gu, Seoul 04383, South Korea
m <- leaflet() %>%
  addTiles() %>%  
  # Specify coordinates for Damascus
  addMarkers(lng=127.378239, lat=35.403609, popup="Kwanghan Pavilion")
m  # Print the map
```
[TOP](#have-fun-in-south-korea)


